My title

### 2022-03-22 outputs/paper/paper.Rmd
survey

>>>>

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s1.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s2.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s3.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s4.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s5.jpg"))
```
